
\documentclass{amsart}
%\usepackage{cmbright}
\usepackage{amsmath, amsfonts, amssymb, amscd}
%\usepackage{tableau}
\usepackage{color}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{array}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{enumerate}




%\oddsidemargin.5cm
%\evensidemargin.5cm
\addtolength{\oddsidemargin}{-.525in}
\addtolength{\evensidemargin}{-.525in}
\addtolength{\textwidth}{1in}

\addtolength{\topmargin}{-.87in}
\addtolength{\textheight}{1.5in}




\newcommand\coolunder[2]{\mathrlap{\smash{\underbrace{\phantom{%
    \begin{matrix} #2 \end{matrix}}}_{\mbox{$#1$}}}}#2}

%\input{tableau}


\newcommand{\+}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\vect}[1]{\boldsymbol{#1}} % Uncomment for BOLD vectors.
%\newcommand{\vect}[1]{\vec{#1}} % Uncomment for ARROW vectors.
\newcommand{\C}{{\mathbb C}}
\newcommand{\Z}{{\mathbb Z}}
\renewcommand{\P}{{\mathbb P}}
\newcommand{\OG}{\operatorname{OG}}
\newcommand{\OF}{\operatorname{OF}}
\newcommand{\bull}{{\scriptscriptstyle \bullet}}
\newcommand{\la}{\lambda}
\newcommand{\euler}[1]{\chi_{_{#1}}}
\newcommand{\cO}{{\mathcal O}}
\newcommand{\cG}{{\mathcal G}}
\newcommand{\cQ}{{\mathcal Q}}
\newcommand{\R}{{\mathbb R}}
\newcommand{\wt}{\widetilde}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\comp}{\operatorname{comp}}
\newcommand{\comment}[1]{}
\newcommand{\type}{\mathfrak{t}}
\newcommand{\op}{\text{op}}
\newcommand{\row}{{\bf r}}
\newcommand{\col}{{\bf c}}
\newcommand{\sym}{\mathfrak{S}}
\newcommand{\codim}{\text{codim}}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}
\renewcommand{\emptyset}{\varnothing}

\newtheorem{thm}{Theorem}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{example}[thm]{Example}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{obs}[thm]{Observation}
\newtheorem{fact}[thm]{Fact}
\newtheorem{remark}[thm]{Remark}
\newtheorem{prob}{Problem}
\newtheorem{chal}{Challenge}

\begin{document}
\title{Problem Set 9}
\date{October 23, 2017}
\author{Intro to Real Analysis}

\maketitle

\begin{prob}
Recall the Chain Rule:
Suppose that $f: A \to \R$ and $g: B \to \R$
satisfy $f(A) \subset B$, that
$f$ is differentiable at $c \in A$,
and that $g$ is differentiable
at $f(c) \in B$.
Then it follows that $g \circ f$
is differentiable at $c$ with
$(g \circ f)'(c) = g'(f(c)) \cdot f'(c)$.
\begin{enumerate}[(a)]
 \item Show that a function $h:A \to \R$
 is differentiable at $a \in \R$
 if and only if there exists a function
 $l: A \to \R$ which is continuous at $a$ and satisfies
 \[
 h(x) - h(a) = l(x)(x-a) \text{ for all } x \in A.
 \]
 \item Use the above criterion
 for differentiability
 to prove the Chain Rule (you will need
 to use both directions of the criterion).
\end{enumerate}
\end{prob}


\begin{prob}
Let
\[f_a(x) =
\begin{cases}
x^a &\text{ if } x > 0\\
0 &\text{ if } x \leq 0,
\end{cases}
\]
for all real numbers $a$.
\begin{enumerate}[(a)]
 \item For which values of $a$ is $f$ continuous at zero?
 \item For which values of $a$ is $f$ differentiable at zero?
In this case, is the derivative function continuous?
\item For which values of $a$ is $f$ twice-differentiable?
\end{enumerate}
\end{prob}

\begin{prob}
 Let
 \[
g_a(x) =
\begin{cases}
x^a \sin(1/x) &\text{ if } x \neq 0\\
0 &\text{ if } x = 0.
\end{cases}
\]
In each part, find one particular value for the number $a$ satisfying the given conditions.  Namely, such that
\begin{enumerate}[(a)]
 \item $g_a$ is differentiable on $\R$ but such that $g'_a$ is unbounded on $[0,1]$.
 \item $g_a$ is differentiable on $\R$ with $g'_a$ continuous but not differentiable at zero.
 \item $g_a$ is differentiable on $\R$ and $g'_a$ is differentiable on $\R$,
 but such that $g_a''$ is not continuous at zero.
\end{enumerate}
\end{prob}


\vspace{5mm}

*All questions taken from \emph{Understanding Analysis: 2nd Edition} by Stephen Abbott.


\end{document}